---
title: "Cleaning Lead Module Evaluation Data"
format: html
editor: visual
---

## Introduction

In this quarto document we will be cleaning the SurveyMonkey data from the LEAD end-of-module evaluation survey.

## Libraries

Some libraries you may not be familiar with - worth knowing about them so check out the links:

-   [here](https://github.com/r-lib/here) gives us the `here()` function, which helps us to locate files consistently and conveniently relative to the repository.

-   [fs](https://github.com/r-lib/fs) gives us some really good file-handling functions like `file_rename()` or `dir_create()`. They are a bit nicer than the base R equivalents.

-   [dplyr](https://dplyr.tidyverse.org/) gives us functions for handling data, such as `select()` or `mutate()`

-   [forcats](forcats.tidyverse.org) is another tidyverse package that helps with handling factors

-   vroom is a package that's really good at reading tabular data from a file

-   

```{r libraries}
library(here)
library(fs)

library(carutools)

library(dplyr)
library(forcats)
library(vroom)
library(janitor)
```

## Load data

This is a great demonstration of the magic of `here::here()` . `responses` are the actual responses to the survey, and `collectors` is a separate table of the collection links that each response came through on. For this survey, respondents had a different collection link depending on which lead module they did, so our first objective is the

```{r load_data}

# TODO: Specify col_types within vroom() (see ?vroom for details)

responses <-
  vroom(
    here("data", "survey-responses_2023-09-22.csv"))

collectors <- 
  vroom(
    here("data", "collector_list.csv"))

# TODO: give data nice names (probably by-hand)
# TODO: Make sure multiple choice questions are encoded as factors, and that all factor levels are accounted for (e.g w/ forcats::fct_expand()). See https://www.surveymonkey.com/r/Preview/?sm=MpKrnloZbwbeGPOOc25qQ_2BSuniu5_2FcloOe2YDuiApcJ6X6fxs9OdnWMpLcKYfIIm for the original forms of all questions

## ^ e.g we want `factor(c(good, bad), levels = c(good, bad, neutral))` - some levels may not be present within the data, only the survey.
```
