---
title: "Cleaning Lead Module Evaluation Data"
format: html
editor: visual
---

## Introduction

In this quarto document we will be cleaning the SurveyMonkey data from the LEAD end-of-module evaluation survey.

## Libraries

Some libraries you may not be familiar with - worth knowing about them so check out the links:

-   [here](https://github.com/r-lib/here) gives us the `here()` function, which helps us to locate files consistently and conveniently relative to the repository.

-   [fs](https://github.com/r-lib/fs) gives us some really good file-handling functions like `file_rename()` or `dir_create()`. They are a bit nicer than the base R equivalents.

-   [dplyr](https://dplyr.tidyverse.org/) gives us functions for handling data, such as `select()` or `mutate()`

-   [forcats](forcats.tidyverse.org) is another tidyverse package that helps with handling factors

-   vroom is a package that's really good at reading tabular data from a file

-   Janitor is great, we like to use it to `clean_names()`

```{r libraries}
library(here)
library(fs)

library(carutools)

library(dplyr)
library(forcats)
library(vroom)
library(janitor)
library(stringr)
```

## Load data

This is a great demonstration of the magic of `here::here()` . `responses` are the actual responses to the survey, and `collectors` is a separate table of the collection links that each response came through on. For this survey, respondents had a different collection link depending on which lead module they did, so our first objective is the

```{r load_data}

responses <-
  vroom(
    
    here("data", "survey-responses_2023-09-22.csv"),
    
    ## 'Response' is meaningless guff in poorly-formatted SM outputs
    na = c("", "NA", "Response"),
    
    col_select =
      c(-`IP Address`, -`Email Address`, -`First Name`,
        -`Last Name`,  -`Custom Data 1`),
    
    col_types =
      
      list(  
        `Respondent ID` = col_character(),
        `Collector ID` = col_character(),
        `Start Date` = col_character(),
        `End Date` = col_character(),
        
        `What do you think were the main strengths and weaknesses of this module?` =
          col_character(),
        
        `How much of this module's learning material was relevant to you?` =
          col_factor(
            levels =
              c("Very little", "Some of it", "Most of it", "All of it")
            ),
        
        `To what extent do you agree with the following statement: "I feel more equipped to lead in my context as a result of my learning through this module."` =
          # sic
          col_factor(c("Strongly disagree", "Disgree", "Agree", "Strongly agree")),

        `Are you interested in the possibility of doing another LEAD module after this one?` =
          col_factor(c("Yes", "No", "Not sure",
                     "I have now completed all the LEAD modules")),
        
        `Has your learning from this module changed your approach to leadership?` =
          col_factor(c("Yes, a great deal", "Yes, somewhat", "Not really")),

        `To what extent do you agree with this statement? "I was given the support and information I needed to complete the learning activities to the best of my ability."` =
          col_factor(c("Strongly disagree", "Disagree", "Agree", "Strongly agree")),
        
        `To what extent do you agree with this statement? \"The feedback I received for my learning activity submissions was helpful"` =
          # sic
          col_factor(c("Strongly disagree", "Disagree", "Aagree", "Strongly agree"))
        )
    )

                  
# TODO: give data nice names (probably by-hand) (dplyr::rename)

```

### Rename data

```{r rename}

## Fix weird SM naming issue ---------------------------------
missing_names <- str_detect(names(responses), "\\.\\.\\.\\d+")

new_names <- 
  responses[1, missing_names] |> 
  unlist() |> 
  unname()

new_names <- str_c(new_names, 1:length(new_names), sep = "_")
names(responses)[missing_names] <- new_names

responses <- slice(responses, -1)

## Rename -----------------------------------------------------
responses <- 
  dplyr::rename(
    responses,
    strengths_and_weaknesses =
      "What do you think were the main strengths and weaknesses of this module?",
    learning_relevance =
      "How much of this module's learning material was relevant to you?",
    equipped_to_lead =
      "To what extent do you agree with the following statement: \"I feel more equipped to lead in my context as a result of my learning through this module.\"",         

    learning_group = "Did you complete this module as part of an action learning group?",                                                                                       
    interested_in_another = "Are you interested in the possibility of doing another LEAD module after this one?",                                                                                  
    changed_approach = "Has your learning from this module changed your approach to leadership?",                                                                                             
    in_what_ways = "You said that this module has changed the way that you approach leadership. In what ways has your approach to leadership changed?",                                   
    given_support = "To what extent do you agree with this statement? \"I was given the support and information I needed to complete the learning activities to the best of my ability.\"",

    helpful_feedback = "To what extent do you agree with this statement? \"The feedback I received for my learning activity submissions was helpful\"",                                       
)

responses <- clean_names(responses)

```

## Save data

```{r save_data}
saveRDS(responses, here("data", "responses_cleaned.RDS"))
```
